Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-18 doc/GMP2015/s07_problempinning.tex
Added Meera's subdivision figure and worked out some of the proof

\begin{figure}\centering
    \begin{subfigure}{0.25\linewidth}
        \includegraphics[width=\linewidth]{img/pentl1}
    \end{subfigure}
    % 
    \begin{subfigure}{0.25\linewidth}
        \includegraphics[width=\linewidth]{img/pentl2}
    \end{subfigure}
    % 
    \begin{subfigure}{0.4\linewidth}
        \includegraphics[width=\linewidth]{img/pentl3}
    \end{subfigure}
    \caption{An example of self-similarity in the form of repeated subdivisions. Each figure follows fromt he previous due to a set subdivision rule. If each figure was guaranteed to be isostatic, then isostatic systems of arbitrary detail could be made.}
    \label{fig:subdivision}
\end{figure}

@@

\begin{theorem}
\label{thm:1dofcase}
    There is a quadratic algorithm for the 1-dof optimal completion problem of Seciton \ref{sec:recomb} for body-pin and multi-triangle-pin graphs.
\end{theorem}

\begin{proof}
    Suppose we are given a body-pin graph and its corresponding body-bar graph $G$ and have obtained the DR-plan $T$. Each node of $T$ will then be a vertex maximal proper 1-dof subgraph of $G$.

@@

    Then, we can form a valid isostatic DR-plan $T_b$ from $T$. In $T_b$, $b$'s children are now all of the leaf nodes of the subtree rooted at $b$ because no child of $b$ in $T$ is isostatic. Similarly, for any other node $w$ that is an ancestor of $b$, $w$'s children will be the node that leads to $b$, denoted $b'$, along with all of the other leaf nodes in the tree rooted at $w$, excluding $b'$. Then, for any node $b$ that we choose, $T_b$ is a valid DR-plan. The size of $T_b$ will just be the maximum fanin of all nodes in $T_b$. Thus, if we want to minimize the size of our DR-plan, we simply need to take the $b$ that has the $T_b$ of smallest size.

    We claim that pinning a new body to a node in the manner described covers all possible ways of adding a new body. Assume we add a new body $b_n$ to our graph and pin it to $b_i$ and $b_j$ to make it isostatic. Then, there will be some lowest 1-dof node $v$ in our tree such that $b_i$ and $b_j$ appear in $v$. This could indeed be the root node. Thus, pinning $v$ in the manner described yields an equivalent isostatic DR-plan to pinning a new body to $b_i$ and $b_j$.

    It is the case that the node we need to pin can wlog be the deepest nontrivial node of some path in $T$. Suppose we chose to pin a node $b$ that has a nontrivial child $v$. Then, $fanin(b)$ is the number of leaves in the subtree rooted at $b$, including the subtree rooted at $v$. If we had instead chosen to pin $v$, then $fanin(b')$ will just be the number of nodes in all its subtrees except for the one rooted at $v$. Then, $\max{fanin(b'),fanin(v)} < fanin(b)$, and for each ancestor $w$ of $b$, $fanin(w)$ is unchanged, meaning $T_v$ has size at most $T_b$. Thus we only have to check the deepest non-trivial nodes.

@@

    Suppose we pin 2 distinct nodes $v_i$ and $v_j$. Then, there will be some common ancestor $a$ of $v_i$ and $v_j$. Then, in $T_{v_i,v_j}$, $fanin(a)$ will be the number of leaves in the subtree rooted at $a$. However, if we chose to pin one of $v_i$ and $v_j$ twice, then $fanin(a)'$ will be the number of leaves in its subtree excluding the subtree containing the node we pinned. Thus $fanin(a)' < fanin(a)$ and the size of $T_{v_i}$ is at most size of $T_{v_i,v_j}$.

@@

% \begin{proof}
%     We can do a similar algorithm to the 1-dof case, except we constrain a given node 2 times (by adding 2 triangles or 2 bodies and 4 pins). This causes the nodes along the path to the given node to become well-constrained while all others will be underconstrained. Thus, our DR-plan will have the same size as the 1-dof case. This is still a quadratic algorithm.

\end{proof}

>>>>

\begin{figure}\centering
    (a)
    \begin{subfigure}{0.2\linewidth}
        \includegraphics[width=\linewidth]{img/pentl1}
    \end{subfigure}
    % 
    $\rightarrow$
    \begin{subfigure}{0.2\linewidth}
        \includegraphics[width=\linewidth]{img/pentl2}
    \end{subfigure}
    %

    (b)
    \begin{subfigure}{0.6\linewidth}
        \includegraphics[width=\linewidth]{img/pentawesome}
    \end{subfigure}
    \caption{Examples of self-similarity in the form of repeated subdivision. In (a), a simple subdivision is done that does not guarantee isostatic. In (b), a more complicated scheme is used, ensuring that the resulting graph is both isostatic and non-tree-decomposable.}
    \label{fig:subdivision}
\end{figure}

@@

\begin{theorem}
\label{thm:1dofcase}
    Given a 1-dof body-pin or multi-triangle graph $G$ and correpsonding 1-dof DR plan $T$, there is a quadratic algorithm for the 1-dof optimal completion problem of Seciton \ref{sec:recomb} for body-pin and multi-triangle-pin graphs.
\end{theorem}

\begin{proof}
    Suppose we are given a body-pin graph and its corresponding body-bar graph $G$ and have obtained the 1-dof DR-plan $T$. Each node of $T$ will then be a vertex maximal proper 1-dof subgraph of $G$.

@@

    Such a pinning covers all possible ways of adding a new body. Assume we add a new body $b$ to our graph and pin it to $b_i$ and $b_j$ to make it isostatic. Then, there will be some lowest 1-dof node $v$ in $T$ such that $b_i$ and $b_j$ appear in $v$. Thus, pinning $v$ in the manner described yields an equivalent isostatic DR-plan to pinning $b$ to $b_i$ and $b_j$.

    For each node $b$, we assign a size of the $T_b$ denoted $|T_b|$. $|T_b| = \displaystyle\max_{v \in T_b} fanin(v)$. We are looking for $b$ that minimizes $|T_b|$. Denote the subtree of $T$ rooted at $v$ by $T^v$ and the number of leaves in a tree $T$ by $nl(T)$. Note that $fanin(b)= nl(T^b)$ because no descendent of $b$ is isostatic. Similarly, for any ancestor $w$ of $b$, $fanin(w) = nl(T^w)-nl(T^{b'})+1$, where $b'$ is the child leading to $b$. All other nodes are not isostatic and so have no fanin.

    % Then, we can form a valid isostatic DR-plan $T_b$ from $T$. In $T_b$, $b$'s children are now all of the leaf nodes of the subtree rooted at $b$ because no child of $b$ in $T$ is isostatic. Similarly, for any other node $w$ that is an ancestor of $b$, $w$'s children will be the node that leads to $b$, denoted $b'$, along with all of the other leaf nodes in the tree rooted at $w$, excluding $b'$. Then, for any node $b$ that we choose, $T_b$ is a valid DR-plan. The size of $T_b$ will just be the maximum fanin of all nodes in $T_b$. Thus, if we want to minimize the size of our DR-plan, we simply need to take the $b$ that has the $T_b$ of smallest size.

    The node we need to pin will always be the deepest nontrivial node of some path in $T$. Suppose we chose to pin a node $b$ that has a nontrivial child $v$. Then, $fanin_b(b) = nl(T^b) = nl(T^v) + n$, where $n$ is essentially the number of leaves between $b$ and $v$. If we had instead chosen to pin $v$, then $fanin_v(b) = nl(T^b) - nl(T^{b'}) + 1 \leq fanin_b(v)$. And for each ancestor $w$ of $b$, $fanin(w)$ is unchanged, meaning $|T_v| \leq |T_b|$. Thus we only have to check the deepest non-trivial nodes.

@@

    Suppose we pin 2 distinct nodes $v_i$ and $v_j$. Then, there will be some common ancestor $a$ of $v_i$ and $v_j$. Then, in $T_{v_i,v_j}$, $fanin_{v_i,v_j}(a) = nl(T^a)$. However, if we chose to pin one of $v_i$ and $v_j$ twice, then $fanin_v(a) = nl(T^a) - nl(T^{a'}) +1$ . Thus $fanin_v(a)' \leq fanin_{v_i,v_j}(a)$. All ancestors of $a$ are unchanged. So $|T_v| \leq |T_{v_i,v_j}|$.

@@

% \begin{proof}
%     We can do a similar algorithm to the 1-dof case, except we constrain a given node 2 times (by adding 2 triangles or 2 bodies and 4 pins). This causes the nodes along the path to the given node to become well-constrained while all others will be underconstrained. Thus, our DR-plan will have the same size as the 1-dof case. This is still a quadratic algorithm.
% \end{proof}
